\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization

### 2010-06-09 honors_thesis/ppsn_paper/paper.tex
Just some formatting, I think
Making the camera ready version for PPSN

Speculative evaluation is made possible by refactoring
PSO such that evaluating the
the objective function is separate from the rest of the computation.  For
simplicity, this discussion will describe the case where PSO is performing
function minimization using the Ring topology.  In this example, each particle
has two neighbors, the ``right neighbor'' and ``left neighbor,'' whose
positions are represented as $\rightn$ and $\leftn$ respectively.  Though we
will only describe the case of the Ring topology, this method is easily
extended to arbitrary topologies.

>>>>

Speculative evaluation is made possible by refactoring PSO such that evaluating
the objective function is separate from the rest of the computation.  For
simplicity, this discussion will describe the case where PSO is performing
function minimization using the Ring topology.  In this example, each particle
has two neighbors, the ``right neighbor'' and ``left neighbor,'' whose
positions are represented as $\rightn$ and $\leftn$ respectively.  Though we
will only describe the case of the Ring topology, this method is easily
extended to arbitrary topologies.
